Disc stuff

### 2012-09-21 paper.tex
added uniform run figs

 \caption{plot of the gridding overlaided on a smoothed density model}
\end{figure}
Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r. For each point to be selected a random number [0-1), $\alpha$ is generated as a threshold. After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$). If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinte is selected. The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest.

fraction of points linear in xyz and unweighted (forces points into outmost regions)
fraction of points forced into the outer half in logarithmic spacing

@@

stuff here
note that all speices show up in absorption and some show a little bit of emission around the edges of the disc
OCS is good for showing up spiral structure
enevelope only contaminates the central plusminus 500 m/s or so

>>>>

 \caption{plot of the gridding overlaided on a smoothed density model}
\end{figure}

\begin{figure}
 \includegraphics[width=84mm]{Figures/model/lime_points_rz.png}

 \caption{plot of the points selected in the model}
\end{figure}

Grid points are selected at random in cylindrical co-ordinates, linearly spaced in z and $\phi$ and logarithmicly spaced in r. For each point to be selected a random number [0-1), $\alpha$ is generated as a threshold. After selection of random co-ordinates the Hydrogen density and molecular density at the point (n and m) are compaired against the densities of a reference point on the inner edge of the disc (n$_0$ and m$_0$). If $\alpha<\left( \frac{n}{n_0} \right)^{0.3}$ or $\alpha< \left( \frac{m}{m_0} \right)^{0.3}$ then the point is selected for use, if not then another r,$\phi$,z co-ordinte is selected. The weighting function and gridding functions were selected empiricly to sample both the all scales while ensuring the majority of the points went into the inner disc which is the region of interest. 20\% of these points are forced to be at radii greater than $\sqrt{R_{min}R_{max}}$ (where $R_{min}$ and $R_{max}$ are the inner and outer radius of the model) in order to stop too many of the selecected points clustering in the high density disc and leaving the envelope undersampled.
In addiation to this method of selection 5\% of the points are randomly distributed about the model with no bias with regards to density or abundance. This provides a minimum level of sampling for the large low density regions in the outer regions of the simulated volume.

@@

note that all speices show up in absorption and some show a little bit of emission around the edges of the disc
OCS is good for showing up spiral structure
enevelope only contaminates the central plusminus 500 m/s or so
